Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-12 hotstorage13/main.tex
ad

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
{\normalsize$^\star$Department of Computer Science, University of California at Santa Barbara}
  {\normalsize$^\dagger$Alibaba Inc.}
}

>>>>

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
{\normalsize$^\star$ University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
}
